\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{tabulary}

\title{LiberIT: Liberty Information Technology Services}
\author{ \hyperref[residential]{Home}
  \hyperref[business]{Business} }

\begin{document}

\maketitle

Would you like help with Computing Services for
  \hyperref[residential]{Home}, \hyperref[business]{Business}
or would you like to 
   \hyperref[contact]{Contact Us}?

\tableofcontents
\section{Contact Us}\label{contact}
\begin{tabulary}{\pagewidth}{rl}
  Name & LiberIT (Liberty Information Technology Services) \\ 
  Email & info@liberit.ca \\
  Phone & 226-256-1632 \\
  Fax & 226-256-8341 \\
\end{tabulary}
\section{Residential Service}\label{residential}

For residential customers LiberIT helps with:

\begin{itemize}
  \item Fixing your internet and WiFi. 
  \item Check on the health of devices. 
  \item Help setting up and maintaining your email.
  \item Showing how to use your computing devices and software. 
  \item Offer consultation for upgrades.
  \item Help setup a backup drive. 
\end{itemize}

\section{Business Service}\label{business}

LiberIT provides the following business services to keep you up and running:

\begin{itemize}
  \item On site service calls for complicated IT issues. 
  \item Keeping your data safe with remote backup. 
  \item Computer hardware and software maintenance and upgrading. 
  \item Rapid resolution to IT problems with remote assistance. 
  \item Preventing IT emergencies and optimizing performance with computer
    health monitoring. 
\end{itemize}

LiberIT also provides the following services to increase sales:
\begin{itemize}
  \item Designing and creating your Sales Funnel. 
  \item Interactive Virtual Receptionist (IVR). 
  \item Ghostwriters for articles and ebooks.
  \item Search Engine Optimization (SEO).
  \item Outsourced telemarketers. 
  \item Phone answering service. 
  \item Website Hosting.
\end{itemize}


%\section{How To Articles}\label{howto}
%\subsection{Do you have a slow computer?}
%\subsection{Have you or are you afraid of losing files?}
%\subsection{Are you getting an error message?}
%\subsection{Do you think you've been hacked?}
%\subsection{Do you need help accessing your email?}
%\subsection{Do you need help with your internet?}
%\subsection{Do you need better wireless reception?}
%\section{Automation and Outsourcing}\label{automate}
%\subsection{Would you like to manage inbound calls?}
%\subsection{Would you like to improve your website?}
%\subsection{Would you like to increase your sales?}
%\subsection{Would you like to automate business processes on your computer?}
\end{document}
