\documentclass[10pt, sigplan, preprint]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{bytefield}
\usepackage{hyperref}
\usepackage{tabulary}
\usepackage{listings}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,automata,petri,positioning}
\pagenumbering{arabic}
\settopmatter{printfolios=true}
\usepackage{fontspec}
\newfontfamily\uni{DejaVu Sans}

\tikzset{place/.style={circle,
        thick,
        draw=blue!75,
        fill=blue!20,
        minimum size=6mm,
    },
    transitionH/.style={rectangle,
        thick,
        fill=black,
        minimum width=8mm,
        inner ysep=2pt
    },
    transitionV/.style={rectangle,
        thick,
        fill=black,
        minimum height=8mm,
        inner xsep=2pt
    }
}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[SLE2017]{SLE Vancouver}{October 2017}{Vancouver, British
Columbia,
Canada} 
\acmYear{2017}
\copyrightyear{2017}

%\acmPrice{15.00}


\begin{document}
\title[]{Pyash: One Language to Unite Them All}
\titlenote{A vertically integrated software language based on the common 
features of the majority of human languages.}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Htaf (Logan) Dwes}
%\authornote{}
\affiliation{%
  \institution{LiberIT Liberty Information Technology Services}
}
\email{logan@liberit.ca}

\renewcommand{\shortauthors}{Logan Dwes}


\begin{abstract}%motivation
    By using the fundamentals of human language, we may be able to achieve
    complete vertical integration for software languages, allowing one language
    to do everything from low level programming to chatting with humans. 

% problem statement
 % Software languages have only been around for a few decades, but due to the
 % limitations of their grammar and vocabulary there has been an explosion of 
 % specialized languages.  At the same time 
  Most
  software languages can't be used for making content, documentation or having a
  discussion. Because the vocabulary and grammar of most software languages is
  so limited, it is impossible to gain conversational fluency, thus they never
  rise to the status of human language, but sit as merely a code. 

% approach
  %By making a language based on the most
  %common features and words of human languages, software languages may become 
  %usable for human discourse and fluency, as well it may become extensible enough
  %that all the various software language purposes could be folded into a single
  %unifying language. 

% results
  After years of research, analysis, data-mining and prototypes, 
  a language has been made that not only allows for human-computer discourse and
  programming, but surprisingly can also be usable as a highly formal 
  pivot language between the majority of human languages. As of this
  writing, beta-testing seems to be just a short time away. 

% conclusion
  In conclusion, a single language to unite all languages is viable at least to
  the degree that it has already been implemented. 
  It can translate between controlled variants of most, possibly all human
  languages. Though further work is needed to prove that those controlled 
  variants can be easily learned by natural language speakers.  It can't 
  translate between different software languages, but may be able to vertically
  integrate all the purposes of software and human languages into one language.
  Further work is needed in order to prove that to a higher degree of certainty.
\end{abstract}

% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

 \begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003124.10010870</concept_id>
<concept_desc>Human-centered computing~Natural language interfaces</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Human-centered computing~Natural language interfaces}

% We no longer use \terms command
%\terms{Theory}

\keywords{grammar, programming language, pivot language}

\include{pyash}
%\input{samplebody-conf.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{pyash} 

\end{document}
